Using Hybrid Machine Learning for Fundamental Stellar Parameter Inference

### 2024-04-23 paper/paper2_neo/paper.tex
Start adding figures to paper

\begin{figure*}[t!]
    \centering
    \includegraphics[width=\textwidth]{images/figure2.png}
    \caption{Heatmap showing how $\ln(a)$ varies over the PHOENIX subset
    slice at solar metallicity. Notice the missing chunk in the top left
    of the figure; \texttt{blase} did not detect a spectral line here,
    but we have to artificially populate those points with lines that 
    have $\ln(a) = -1000$.}
\end{figure*}

\subsection{Continuously Evaluable Manifolds}
For each line, the inputs to the interpolator were the three input parameters $T_{\mathrm{eff}}$,
$\log(g)$, and [Fe/H], and the output was a list of four parameters, 
$\mu'$, $\ln(a)$, $\sigma$, and $\gamma$. For each line, one of these 
interpolator objects was created using linear interpolation, and these 
interpolators were aggregated into a single list, which was when pickled 
and written to a \texttt{.pkl} file. These interpolators generate multiple 
manifolds with the following mapping:
\begin{gather}
    \mqty[T_{\mathrm{eff}} \\ \log(g) \\ \mathrm{[Fe/H]}] \rightarrow \mqty[\mu' \\ \ln(a) \\ \sigma \\ \gamma]
\end{gather}
These interpolators could now be evaluated at any point lying within the 
domain of the PHOENIX subset, turning a discretely sampled PHOENIX subset 
into a continuous one. With the given size of the PHOENIX subset, the 
interpolator list takes up 13.2 GB of disk space. Since this is now evaluable,
we call this the PHOENIX generator.

@@

\subsection{Performance Results}
Text

>>>>

\begin{figure*}[t!]
    \centering
    \includegraphics[width=\textwidth]{images/figure2.png}
    \caption{Heatmap showing how $\ln(a)$ and $\sigma$ vary over the PHOENIX subset
    slice at solar metallicity. Notice the missing chunk in the top left
    of the figure; \texttt{blase} did not detect a spectral line here,
    but we have to artificially populate those points with lines that 
    have $\ln(a) = -1000$.}
\end{figure*}

\subsection{Continuously Evaluable Manifolds}
For each line, the inputs to the interpolator were the three input parameters $T_{\mathrm{eff}}$,
$\log(g)$, and [Fe/H], and the output was a list of four parameters, 
$\mu'$, $\ln(a)$, $\sigma$, and $\gamma$. For each line, one of these 
interpolator objects was created using linear interpolation, and these 
interpolators were aggregated into a single list, which was when pickled 
and written to a \texttt{.pkl} file. These interpolators generate multiple 
manifolds with the following mapping:
\begin{gather}
    \mqty[T_{\mathrm{eff}} \\ \log(g) \\ \mathrm{[Fe/H]}] \rightarrow \mqty[\mu' \\ \ln(a) \\ \sigma \\ \gamma]
\end{gather}
These interpolators could now be evaluated at any point lying within the 
domain of the PHOENIX subset, turning a discretely sampled PHOENIX subset 
into a continuous one. With the given size of the PHOENIX subset, the 
interpolator list takes up 13.2 GB of disk space. This evaluation 
is able to reconstruct an existing PHOENIX spectrum or alternatively 
interpolate a new spectrum within the domain of the PHOENIX subset,
we call this the PHOENIX generator.

@@

\subsection{Spectral Reconstruction Time}
Typically a practitioner would wish to use a reconstruction in an iterative 
way, repeatedly generating spectra from input (teff, logg, FeH) 
coordinates.  Therefore, there is a strong desire to bring the computational 
cost of reconstruction to extremely low values close to subsecond.
We evaluate the computational time of our generator in two ways.  First, 
for a single input. When evaluating a vector of inputs, we parallelize the interpolator evaluation, 
however the reconstruction done by \texttt{blase} on each evaluated state 
dictionary is done serially.

The single input performance 
takes $\sim$30 seconds, which is much too large for typical Bayesian inference procedures.

I hand in a (teff, logg, FeH) pair, how long does it take to get back a reconstructed spectrum?

\subsection{Bayesian Optimizer Accuracy}
TACC
